Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
minor edits in section 4.2

In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions. 
For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
For each red giant, the mass-loss rate is estimated by the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
%%%
\begin{equation}
\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
\end{equation}
%%%
where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$, $\tilde R = R_{\star }/R_{\odot }$, $\tilde M = M_{\star }/M_{\odot }$, and $g$ is the surface gravity. 
The velocity of the stellar wind is assumed to be the escape velocity at $\sim 4 R_{\star }$:
%%%
\begin{equation}
v \sim \sqrt{\frac{2GM_\star}{4R_{\star }}}
\end{equation}
%%%
The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass. We simply assume:
%%%
\begin{equation}
t \sim 10\,{\rm Gyr}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{-2.5}
\end{equation}
%%%
Combining this relation with equations (\ref{eq:fcyc}) and (\ref{eq:scalingB}) results in
%%%
\begin{equation}
\nu_{\rm cyc,\,max} \sim 20 \,{\rm MHz}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{1.075} \left( \frac{M_p}{M_{p,\,{\rm J}}} \right)^{1.04} 
\end{equation}
%%%
In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}.

@@

Figure \ref{fig:observability} displays the estimated radio flux from Jupiters [A] and [B] around M-type red giants within 300~pc. 
Jupiters are placed at 1 AU and at 5 AU for reference. 
The difference of the symbols indicates whether the radio emission can escape from the system (circle), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$,  or not (cross). 
Assuming Jupiter-mass planets which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, a reasonable number of systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while the those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind. 
For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth. $10~M_{\rm J}$ planets at $\sim 1$ AU will be detectable out to $\sim 200$~pc.

>>>>

In order to examine the realistic potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions. 
For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
For each red giant, the mass-loss rate is estimated using the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
%%%
\begin{equation}
\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
\end{equation}
%%%
where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$ is the stellar luminosity, $\tilde R = R_{\star }/R_{\odot }$ is the stellar radius, $\tilde M = M_{\star }/M_{\odot }$ is the stellar mass, and $g$ is the surface gravity. 
The velocity of the stellar wind is assumed to be the escape velocity at $\sim 4 R_{\star }$:
%%%
\begin{equation}
v \sim \sqrt{\frac{2GM_\star}{4R_{\star }}}
\end{equation}
%%%
The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass. We simply assume:
%%%
\begin{equation}
t \sim 10\,{\rm Gyr}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{-2.5}
\end{equation}
%%%
Combining this relation with equations (\ref{eq:fcyc}) and (\ref{eq:scalingB}) results in
%%%
\begin{equation}
\nu_{\rm cyc,\,max} \sim 20 \,{\rm MHz}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{1.075} \left( \frac{M_p}{M_{p,\,{\rm J}}} \right)^{1.04} 
\end{equation}
%%%
In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}.

@@

Figure \ref{fig:observability} displays the estimated radio flux from Jupiters [A] and [B] around M-type red giants within 300~pc. 
Jupiters are placed at 1 AU and at 5 AU for reference. 
The difference of the symbols indicates whether the radio emission can escape from the system (circle), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$,  or not (cross). 
Assuming Jupiter-mass planets which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, a reasonable number of systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind. 
For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth. $10~M_{\rm J}$ planets at $\sim 1$ AU may be detectable out to $\sim 200$~pc.
